### 2019-04-30 report/papers.tex
23 pages

\paragraph{Computation}
By duality theory he obtained that to $\alpha$, corresponds a value $\lambda \geqslant 0$ such that the distance $d_{M, \alpha}$ is equal to the distance $d_M^\lambda$ defined by:
$$ d_M^\lambda(a, b) = \langle P^\lambda, M \rangle, \quad \text{where } P^\lambda = \argmin_{P \in U(a, b)} \langle P, M \rangle - \dfrac{1}{\lambda} H(P) $$
Then Cuturi show that this new distance can be computed with a much cheaper cost than the original Wassertein distance.

\sect{Wasserstein GAN}

\cite{Arj++}

@@

\paragraph{Applications}
This has many applications in geometric domains. Applications that are given are:
\begin{itemize}
	\item Shape interpolation (\figurename~\ref{shape})
		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.22]{shape_int.png}
			\caption{Application to shape interpolation}
			\label{shape}
		\end{figure}
	\item BRDF design
	\item Color histogram manipulation
	\item Skeleton layout
	\item Soft maps
\end{itemize}
Finally here are two images of barycenters they have computed. The first one is an image where we find barycenters of four images that are in the corners. The second is an interpolation between two cards. As we tried to reproduce it in the implementation part we put them here :

>>>>

\paragraph{Computation}
By duality theory he obtained that to $\alpha$, corresponds a value $\lambda \geqslant 0$ such that the distance $d_{M, \alpha}$ is equal to the distance $d_M^\lambda$ defined by:
$$ d_M^\lambda(a, b) = \langle P^\lambda, M \rangle, \quad \text{where } P^\lambda = \argmin_{P \in U(a, b)} \langle P, M \rangle - \dfrac{1}{\lambda} H(P) $$
Then Cuturi show that this new distance can be computed with a much cheaper cost than the original Wassertein distance $d_M$. In fact the iterative Sinkhorn algorithm presented below converge in few steps to the transport plan $P^\lambda$. The \figurename~\ref{recap1} summarize the relationships between all these distances.

\vspace{3mm}
\begin{algorithm}[H]
	\caption{\textsc{Sinkhorn}$\left( a, \{ b_i \}_{i=1}^N, M, \lambda \right)$}
	$B \gets \left[ b_1, \dots, b_N \right] \in \R^{n \times N}$ \;
	$K \gets \exp \left( \lambda M \right)$ \;
	$u = \left[ u_1, \dots, u_N \right] \gets \mathbbm{1}_{n \times N} \, / \, n$ \;
	\Repeat{convergence of $u$}{
		$u \gets a \, / \, \left( K \left( B \, / \, \left( K^\trans u \right) \right) \right)$ \;
	}
	$v = \left[ v_1, \dots, v_N \right] \gets B \, / \, \left( K^\trans u \right)$ \;
	$P^\lambda_i \gets \text{diag}(u_i) K \text{diag}(v_i)$ \;
	\Return $d = \left[ d_M^\lambda(a, b_1), \dots, d_M^\lambda(a, b_N) \right] = \left[ \left\langle M, P^\lambda_1 \right\rangle, \dots, \left\langle M, P^\lambda_N \right\rangle \right]$
\end{algorithm}
\vspace{3mm}

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{recap1.png}
	\captionsetup{justification=centering}
	\caption{Graphical representation of different distances and their relationships.}
	\label{recap1}
\end{figure}

\paragraph{Results}
The regularized Wasserstein distance is then used in a SVM to classifiy images of the MNIST database. The \figurename~\ref{comp} compare the error on a test set for different distances used in the SVM. The distance EMD is the classical optimal transport. As we can see the regularized version beat all distances. Furthermore he evaluated the execution time by stopping the iterations when $\| d_{i+1} / d_i - 1 \| < 10^{-4}$ where $d_i$ is the distance obtained at the end of the iteration $i$. He gave a comparison between EMD and regularized Wasserstein for different values of $\lambda$ in the \figurename~\ref{comp2}.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.55]{comp.png}
	\caption{Test error for different distances}
	\label{comp}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{comp2.png}
\caption{Execution time for different distances}
\label{comp2}
\end{figure}

\newpage

\sect{Wasserstein GAN \cite{Arj++}}

@@

\paragraph{Applications}
This has many applications in geometric domains. Applications that are given are:
\begin{itemize}
	\item Shape interpolation (\figurename~\ref{shape})
		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.22]{shape_int.png}
			\caption{Application to shape interpolation}
			\label{shape}
		\end{figure}
	\item BRDF design
	\item Color histogram manipulation
	\item Skeleton layout
	\item Soft maps
\end{itemize}
Finally \figurename~\ref{barp} and \figurename~\ref{cardp} are two images of barycenters they have computed. The first one is an image where we find barycenters of four images that are in the corners. The second is an interpolation between two cards. As we tried to reproduce it in the implementation part we put them here:
